---
title: "Analysis of Website C Data"
author: "Sanket Achari"
date: "Tuesday, April 21, 2015"
output: html_document
---

### Insights of following parameters are present in this report
- Reach
- Impression 
- Clicks, Clicks Through Rate (CTR)
- Likes, Comments & Shares


```{r,echo=FALSE, warning=FALSE, cache=TRUE, message=FALSE,comment= NA}
library(xlsx)
library(dplyr)
library(ggplot2)
data <- read.xlsx("Data Analytics case study.xlsx",sheetName = "Sheet1")
names(data)[8] <- paste("CTR")
columns <- colnames(data)
```


```{r, echo=FALSE}
webC_data <- data[which(data$Website == "Website C"),]
```


### Reach 
```{r,echo=FALSE, cache =TRUE,message=FALSE ,fig.height= 8, fig.width= 12, fig.align='center'}
g1 <- ggplot(webC_data, aes(x = Post.about,y = Reach/1000, fill = Post.about))+
      geom_bar(stat = "identity", col= "black", width = 1) + 
      theme(axis.text.x = element_text(angle = 60,hjust = 1)) +
      xlab("Mobile Phones") + ylab("Reach in thousands") +
      ggtitle("Website - C Reach Vs Mobile Phones")
g1

```

 Top 5 posts which has got maximum Reach
```{r, echo=FALSE,comment= NA}
webC_Reach <- webC_data[order(webC_data$Reach,decreasing = TRUE), ] 
print(webC_Reach[1:5,c(1,2,4)],row.names = FALSE)
```

Top 5 posts which has got minimum Reach
```{r, echo=FALSE,comment= NA}
webC_Reach <- webC_data[order(webC_data$Reach,decreasing = FALSE), ] 
print(webC_Reach[1:5,c(1,2,4)],row.names = FALSE)
```

### Impression


Top 3 posts which has got maximum Impressions
```{r, echo=FALSE,comment= NA}
webC_Impressions <- webC_data[order(webC_data$Impressions,decreasing = TRUE), ] 
print(webC_Impressions[1:3,c(1,2,6)],row.names = FALSE)
```

Top 3 posts which has got minimum Impressions
```{r, echo=FALSE,comment= NA}
webC_Impressions <- webC_data[order(webC_data$Impressions,decreasing = FALSE), ] 
print(webC_Impressions[1:3,c(1,2,6)],row.names = FALSE)
```


### Clicks
```{r, echo=FALSE, cache =TRUE,message=FALSE ,fig.height= 6.5, fig.width= 12, fig.align='center'}
g2 <- ggplot(webC_data, aes(x = Post.about,y = Clicks/100, fill = Post.about))+
      geom_bar(stat = "identity", col= "black", width = 1) + 
      theme(axis.text.x = element_text(angle = 60,hjust = 1)) +
      xlab("Mobile Phones") + ylab("Clicks in hundreds") +
      ggtitle("Website - C Clicks Vs Mobile Phones")
g2

```

Top 5 posts which has got maximum Clicks
```{r, echo=FALSE,comment= NA}
webC_Clicks <- webC_data[order(webC_data$Clicks,decreasing = TRUE), ] 
print(webC_Clicks[1:5,c(1,2,7)],row.names = FALSE)
```

Top 5 posts which has got minimum Clicks
```{r, echo=FALSE,comment= NA}
webC_Clicks <- webC_data[order(webC_data$Clicks,decreasing = FALSE), ] 
print(webC_Clicks[1:5,c(1,2,7)],row.names = FALSE)
```

### Click- Through Rate (CTR)

```{r,echo=FALSE,cache =TRUE,message=FALSE ,fig.height= 6, fig.width= 12, fig.align='center'}
g3 <- ggplot(webC_data, aes(x = Post.about,y = CTR, 
                            fill = Post.about))+ 
      geom_bar(stat = "identity", col= "black", width = 1) +
      theme(axis.text.x = element_text(angle = 60,hjust = 1)) +
      xlab("Mobile Phones") + ylab("Click- Through Rate (CTR)") +
      ggtitle("Website - C  Click- Through Rate (CTR) Vs Mobile Phones")
g3

```


Top 5 posts which has got maximum Click- Through Rate (CTR)
```{r, echo=FALSE,comment= NA}
webC_CTR <- webC_data[order(webC_data$CTR,decreasing = TRUE), ] 
print(webC_CTR[1:5,c(1,2,8)],row.names = FALSE)
```

Top 5 posts which has got minimum Click- Through Rate (CTR)
```{r, echo=FALSE,comment= NA}
webC_CTR <- webC_data[order(webC_data$CTR,decreasing = FALSE), ] 
print(webC_CTR[1:5,c(1,2,8)],row.names = FALSE)
```


### Likes

### Highest Likes on the post
```{r, echo=FALSE}
webC_Likes <- webC_data[order(webC_data$Post.Likes,decreasing = TRUE), ] 
webC_Likes <- webC_Likes[1:10,] 
```

```{r,echo=FALSE,cache =TRUE,message=FALSE ,fig.height= 6, fig.width= 6, fig.align='center'}
g4 <- ggplot(webC_Likes, aes(reorder(Post.about,desc(Post.Likes)),Post.Likes))+
      geom_bar(stat = "identity", width = 1, color = "black", fill = "darkgreen") + 
      theme(axis.text.x = element_text(angle = 60,hjust = 1)) +
      xlab("Mobile Phones") + ylab("Number of Likes") +
      ggtitle("Website - C Number of Likes Vs Mobile Phones")
g4

```
```{r, echo=FALSE,comment= NA}
print(webC_Likes[1:5,c(1,2,9)],row.names = FALSE)
```


### Lowest Likes on the post

```{r,echo=FALSE,cache =TRUE,message=FALSE ,fig.height= 6, fig.width= 6, fig.align='center',comment= NA}
webC_Likes <- webC_data[order(webC_data$Post.Likes,decreasing = FALSE), ] 
webC_Likes <- webC_Likes[1:10,] 

g5 <- ggplot(webC_Likes, aes(reorder(Post.about,-desc(Post.Likes)),Post.Likes))+
      geom_bar(stat = "identity", width = 1, color = "black", fill = "red") + 
      theme(axis.text.x = element_text(angle = 60,hjust = 1)) +
      xlab("Mobile Phones") + ylab("Number of Likes") +
      ggtitle("Website - C Number of Likes Vs Mobile Phones")
g5

print(webC_Likes[1:5,c(1,2,9)],row.names = FALSE)
```




### Comments

### Highest Comments on the post

```{r,echo=FALSE,cache =TRUE,message=FALSE ,fig.height= 8, fig.width= 8, fig.align='center',comment= NA}
webC_Comments <- webC_data[order(webC_data$Post.Comments,decreasing = TRUE), ] 
webC_Comments <- webC_Comments[1:10,] 

g4 <- ggplot(webC_Comments, aes(reorder(Post.about,desc(Post.Comments)),Post.Comments))+
      geom_bar(stat = "identity", width = 1, color = "black", fill = "darkgreen") + 
      theme(axis.text.x = element_text(angle = 60,hjust = 1)) +
      xlab("Mobile Phones") + ylab("Number of Comments") +
      ggtitle("Website - C Number of Comments Vs Mobile Phones")
g4

print(webC_Comments[1:5,c(1,2,10)],row.names = FALSE)
```

### Many posts have got zero comments
```{r,echo=FALSE,cache =TRUE,message=FALSE ,fig.height= 6, fig.width= 6, fig.align='center',comment= NA}
webC_Comments <- webC_data[order(webC_data$Post.Comments,decreasing = FALSE), ] 
webC_Comments <- webC_Comments[1:10,] 
print(webC_Comments[1:5,c(1,2,10)],row.names = FALSE)
```


### Highest Shares of the post

```{r,echo=FALSE,cache =TRUE,message=FALSE ,fig.height= 6, fig.width= 6, fig.align='center',comment= NA}
webC_Shares <- webC_data[order(webC_data$Post.Shares,decreasing = TRUE), ] 
webC_Shares <- webC_Shares[1:10,] 
print(webC_Shares[1:5,c(1,2,11)],row.names = FALSE)
```

### Many posts have got zero shares
```{r,echo=FALSE,cache =TRUE,message=FALSE ,fig.height= 6, fig.width= 6, fig.align='center',comment= NA}
webC_Shares <- webC_data[order(webC_data$Post.Shares,decreasing = FALSE), ] 
webC_Shares <- webC_Shares[1:10,] 
print(webC_Shares[1:5,c(1,2,11)],row.names = FALSE)
```
